Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-02 Moltres.tex
Combine moltres and msre lines in one plot.

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

\begin{figure}[htpb]
    \centering
    \begin{subfigure}[b]{.5\textwidth}
      \includegraphics[width=\maxwidth{\textwidth}]{fuel_vs_moderator_axial_sweep.eps}
      \caption{Moltres predicted axial temperature profiles in hottest channel
        and adjacent graphite}
      \label{fig:moltres_axial_temps}
    \end{subfigure}
    %\quad
    \begin{subfigure}[b]{.5\textwidth}
      \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_temps.png}
      \caption{\gls{MSRE} design axial temperature profiles in hottest channel
        and adjacent graphite stringer \cite[p. 99]{briggs_molten-salt_1964}}
      \label{fig:msre_axial_temps}
    \end{subfigure}
    \caption{Comparison of \gls{MSRE} design and Moltres predicted axial
      temperature profiles}
    \label{fig:temp_compare}
\end{figure}

\Cref{fig:moltres_radial_fluxes} compares the fast and thermal neutron fluxes at the
reactor mid-plane ($z=H/2$). Local thermal flux growth and fast flux decay in
moderator regions and visa versa in fuel regions are apparent. The flux
magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
calculations \cite[p. 92]{briggs_molten-salt_1964} as shown in
\cref{fig:msre_radial_fluxes}. The peak fast to thermal flux ratio is
approximately 3.5 in the \gls{MSRE} design calculation as opposed to a ratio of
3 for the Moltres calculation. Control rod thimbles and
an extra volume of surrounding fuel not included in the Moltres calculations
cause the depression in the thermal flux in \cref{fig:msre_radial_fluxes}.

\begin{figure}[htpb]
    \centering
    \begin{subfigure}[b]{.5\textwidth}
      \includegraphics[width=\maxwidth{\textwidth}]{moltres_radial_fluxes.eps}
      \caption{The thermal and fast flux profiles at the core mid-plane
        ($z=H/2$) for Moltres 2-D cylindrical axisymmetric model ($r=0$ is radial center
        of core)}
      \label{fig:moltres_radial_fluxes}
    \end{subfigure}
    %\quad
    \begin{subfigure}[b]{.5\textwidth}
      \includegraphics[width=\maxwidth{\textwidth}]{msre_radial_fluxes.png}
      \caption{The thermal and fast flux profiles at the core mid-plane
        ($z=H/2$) for \gls{MSRE} design model \cite{briggs_molten-salt_1964}
        ($r=0$ is radial center of core)}
      \label{fig:msre_radial_fluxes}
    \end{subfigure}
    \caption{Comparison of \gls{MSRE} design and Moltres predicted radial
      flux profiles}
    \label{fig:radial_fluxes_compare}
\end{figure}

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the
plots are chosen to correspond to the peak of the thermal flux in both cases;
for the \gls{ORNL} calculations this is 8.4 inches from the core center-line
because of the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the plot in \cref{fig:msre_axial_fluxes}
extends to lower and higher z-values than
\cref{fig:moltres_axial_fluxes}. Additionally, absorption in the plena caused 
deviation of the thermal flux from a sinusoidal shape in 
\cref{fig:msre_axial_fluxes}.

\begin{figure}[htpb]
    \centering
    \begin{subfigure}[b]{.5\textwidth}
      \includegraphics[width=\maxwidth{\textwidth}]{moltres_axial_fluxes.eps}
      \caption{Moltres axial flux profiles along core center line}
      \label{fig:moltres_axial_fluxes}
    \end{subfigure}
    %\quad
    \begin{subfigure}[b]{.5\textwidth}
      \includegraphics[width=\maxwidth{\textwidth}]{msre_axial_fluxes.png}
      \caption{\gls{MSRE} design axial flux profiles 8.4 inches from the core
        center line \cite{briggs_molten-salt_1964}}
      \label{fig:msre_axial_fluxes}
    \end{subfigure}
    \caption{Comparison of \gls{MSRE} design and Moltres predicted axial
      flux profiles}
    \label{fig:axial_fluxes_compare}
\end{figure}

>>>>

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profile shapes are in decent qualitative agreement with both Moltres and
\gls{MSRE} calculations showing a peak in graphite temperature before the
reactor outlet. Fuel temperature increases monotonically in both Moltres and
\gls{MSRE} models. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model 
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial_temps.eps}
    \caption{Moltres and \gls{MSRE} design
      \cite[p. 99]{briggs_molten-salt_1964} predicted axial temperature profiles in hottest channel
      and adjacent graphite}
    \label{fig:temp_compare}
\end{figure}

\Cref{fig:radial_fluxes_compare} compares the fast and thermal neutron fluxes at
the reactor mid-plane ($z=H/2$) for Moltres and \gls{MSRE} design models. Local
thermal flux growth and fast flux decay in moderator regions and visa versa in
fuel regions are apparent in the Moltres calculation. The Moltres flux
magnitudes are in good agreement with the magnitudes from the \gls{MSRE} design
calculations \cite[p. 92]{briggs_molten-salt_1964}. The peak fast to thermal
flux ratio is approximately 3.5 in the \gls{MSRE} design calculation as opposed
to a ratio of 3 for the Moltres calculation. Control rod thimbles and an extra
volume of surrounding fuel not included in the Moltres calculations cause the
depression in the thermal flux in the \gls{MSRE} profile.

\begin{figure}[htpb]
    \centering
      \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_radial.eps}
      \caption{The thermal and fast flux profiles at the core mid-plane
        ($z=H/2$) for the Moltres 2-D cylindrical axisymmetric model and the
        \gls{MSRE} design model \cite[p. 92]{briggs_molten-salt_1964} ($r=0$ is
        radial center of core).}
    \label{fig:radial_fluxes_compare}
\end{figure}

\Cref{fig:axial_fluxes_compare} compares the axial flux profiles calculated by
Moltres and the \gls{ORNL} \gls{MSRE} design model. The radii for the plots are
chosen to correspond to the peak of the thermal flux in both cases; for the
\gls{ORNL} calculations this is 8.4 inches from the core center-line because of
the effect of the control rod thimbles and extra fuel along the
center-line. Once again, the plots are in decent agreement. The \gls{ORNL}
calculations include the lower and upper plena which are not included in this
report's Moltres model. Consequently, the \gls{MSRE} lines extend to lower and
higher z-values than the Moltres lines. Additionally, absorption
in the plena cause deviation of the thermal flux from a sinusoidal shape in the
\gls{MSRE} design case.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=\maxwidth{\textwidth}]{combined_msre_moltres_axial.eps}
    \caption{Moltres axial flux profiles along core center line and \gls{MSRE}
      design axial flux profiles 8.4 inches from core center line \cite[p. 91]{briggs_molten-salt_1964}.}
    \label{fig:axial_fluxes_compare}
\end{figure}
